Notes on generating initial models for mapping into {\tt MAESTRO}

### 2008-08-19 docs/initial_models/paper.tex
added some notes to myself about what needs to be done

% Margins
\usepackage[lmargin=0.5in,rmargin=0.5in,tmargin=0.75in,bmargin=0.75in]{geometry}

@@

\section{Creating the initial model}
\begin{itemize}
\item The initial model should be but into HSE according to 
$(p_{i+1} - p_i)/\Delta r = \half (\rho_{i+1} - \rho_i) g_{i+\half} \enskip .$

\item The initial model should be created at the same resolution as
the base state.  This means that when you change resolution of your
simulation, use a new initial model.

\item The initial model should be thermodynamically consistent with
the EOS that {\tt MAESTRO} uses.

\end{itemize}

\section{Spherical notes}
\begin{itemize}
\item Spherical runs use $p$, $(\rho X)$, and $\rho$ from the initial
model.  These are then mapped onto the Cartesian grid, and then
$(\rho h)$ is computed via the EOS.

\item Spherical runs automatically set $\Delta x = \Delta r$.
\end{itemize}

\section{Running notes}
\begin{itemize}
\item When the code is run, it prints out the HSE error of the base
state model---this should be checked to insure that we a
\end{itemize}

\end{document}

>>>>

% Margins
\usepackage[lmargin=0.5in,rmargin=1.5in,tmargin=0.5in,bmargin=0.5in]{geometry}

@@

\section{Initialization Procedure}
\subsection{Creating the Initial Model}
We denote the initial model returned by the code in the {\tt MAESTRO/initial\_models} directory with the superscript ``init''.
\begin{itemize}
\item Include a table of which file creates initial models for which examples.
\item Indicate which variables are returned by the initial model.
\item Describe how the initial model is developed such that the pressure and density are in hydrostatic equilibrium.
\end{itemize}
\subsection{Initialization Procedure}
Given data from an initial model file (indicated with a superscript ``init''), this section describes how the base state ($\rho_0$, $p_0$) and full state are computed.

\section{Old Notes}
\subsection{Creating the initial model}
\begin{itemize}
\item The initial model should be but into HSE according to 
$(p_{i+1} - p_i)/\Delta r = \half (\rho_{i+1} - \rho_i) g_{i+\half} \enskip .$
\item The initial model should be created at the same resolution as
the base state.  This means that when you change resolution of your
simulation, use a new initial model.
\item The initial model should be thermodynamically consistent with
the EOS that {\tt MAESTRO} uses.
\end{itemize}
\section{Spherical notes}
\begin{itemize}
\item Spherical runs use $p$, $(\rho X)$, and $\rho$ from the initial
model.  These are then mapped onto the Cartesian grid, and then
$(\rho h)$ is computed via the EOS.
\item Spherical runs automatically set $\Delta x = \Delta r$.
\end{itemize}
\section{Running notes}
\begin{itemize}
\item When the code is run, it prints out the HSE error of the base
state model---this should be checked to insure that we a
\end{itemize}
\end{document}
